A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-12-12 manuscript.Rmd
name correct directory
adjust hashing #4

```{r}
x <- data.frame(VAR1=c(1,2,3,4),VAR2=c(0,4,6,9) )
checksum <- digest::sha1(x)
if (checksum != "bd4b9197ff7f8e32e56b9d62c3ee7718f367b485"){
  warning("Wrong data file loaded or data has been changed!")
}
```

@@

```{bash, eval=FALSE}
git clone https://github.com/aaronpeikert/workflow-showcase.git
cd reproducible-research
make build
make all DOCKER=TRUE
```

>>>>

```{r}
x <- data.frame(VAR1=c(1,2,3,4),VAR2=c(0,4,6,9) )
checksum <- digest::digest(x, "sha1")
if (checksum != "8e222b9b3616595dc3f5946f9eac101fbf1336dc"){
  warning("Mismatch between original and current data file!")
}
```

@@

```{bash, eval=FALSE}
git clone https://github.com/aaronpeikert/workflow-showcase.git
cd workflow-showcase
make build
make all DOCKER=TRUE
```
